clusters

### 2015-07-16 cluster.rmd
knn start

# library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

code.contact
code.client
Project.Value
JD.Second
Billing.Type
Post.Code
code.ProjEng
Billing.Type
majority.pos
pc.majpos

@@

all7d<- all7c %>% select(inv.mlsto, timespan, no.users, Discipline, pc.pro, client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Billing.Type, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos)

@@

>>>>

# library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
library('FNN')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

code.contact
code.client
Project.Value
JD.Second
Post.Code
code.ProjEng
Billing.Type
majority.pos
pc.majpos

@@

all7d<- all7c %>% select(inv.mlsto, timespan, no.users, Discipline, pc.pro, 
                         client.totinv, code.director, 
                         Num.disc, Business,
                         Biz.type, code.contact, pc.majpos,
                         code.client, Project.Value, JD.Second, Post.Code, code.ProjEng, 
                         Billing.Type, majority.pos)

@@

Say we are trying to retrieve the nearest neighbours.
There will be two types of distances:

* numerical nearest neighbours
* categorical nearest neighbours

Which numerical categories would we want to include in the nearest neighbour search?

No NA:
* inv.mlsto
* timespan
* no.users
* Num.disc
* pc.pro
* client.totinv
Discipline
code.director
Business
Biz.type

* pc.majpos
* Project.Value
code.contact
code.client
JD.Second
Post.Code
code.ProjEng
Billing.Type
majority.pos
